### 2019-04-02 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
new structure

\section{Electro-Mechanical Spinning}
A number of techniques have being develop for the fabrication of nano-fibers, such as arc discharge [22], chemical vapor deposition, laser ablation [23], and vapor growth [21]. Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required. The electrospinning method can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$

Diverse polymer patterning techniques have been developed to integrate and synthesize carbon nano-wires. A typical technique is electrospinning. Electrospinning requires the application of an electrostatic force to a polymer solution to spin fibers. The applied electric field, the solution conductivity, jet length, solution viscosity surrounding gas, flow rate and the collector geometry are important parameters that influence the fiber formation during the spinning. \cite{Nataraj2012} Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the
tip is called NFES or near-field electrospinning. \cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning. \cite{Nataraj2012}

\section{Carbon nano-fibers}
Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand nm; composed mostly by carbon atoms aligned parallel to the long axis of the fiber. \cite{Nataraj2012} Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form. \cite{Nataraj2012}

>>>>

\section{Electro-Mechanical Spinning}
Diverse polymer patterning techniques have being develop for the fabrication of nano-fibers, such as arc discharge [22], chemical vapor deposition, laser ablation [23], and vapor growth [21]. Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required. The electrospinning method can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$ [24,25] from a polymer solution under the influence of an electrostatic force. The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry [26-30]. [31-33]

\cite{Nataraj2012}

Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning. \cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning. \cite{Nataraj2012}

\section{Carbon nano-wire}
Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand nm; composed mostly by carbon atoms aligned parallel to the long axis of the fiber. \cite{Nataraj2012} Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form. \cite{Nataraj2012}
